Bayesian analysis of the NESTA study of interventions against verbal aggression online \linebreak Technical Report

### 2021-12-21 technicalReport/technicalReport4.tex
started technical report

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  10pt,
  dvipsnames,enabledeprecatedfontcommands]{scrartcl}
\title{Bayesian analysis of the NESTA study of interventions against
verbal aggression online}
\author{Rafal Urbaniak}
\date{}

@@

  pdftitle={Bayesian analysis of the NESTA study of interventions against verbal aggression online},

@@

\setcounter{secnumdepth}{5}
%\documentclass{article}

% %packages
 \usepackage{booktabs}

@@

\usepackage{longtable}
\usepackage{ragged2e}
\usepackage{etex}
%\usepackage{yfonts}
\usepackage{marvosym}
\usepackage[notextcomp]{kpfonts}
\usepackage{nicefrac}
\newcommand*{\QED}{\hfill \footnotesize {\sc Q.e.d.}}
\usepackage{floatrow}

\usepackage[textsize=footnotesize]{todonotes}
%\linespread{1.5}
\usepackage{pdfpages}
\setlength{\parindent}{10pt}
\setlength{\parskip}{1pt}

%language
\usepackage{times}
\usepackage{t1enc}
%\usepackage[utf8x]{inputenc}
%\usepackage[polish]{babel}
%\usepackage{polski}
\usepackage[utf8]{inputenc}
\usepackage{mathptmx}
\usepackage[scaled=0.88]{helvet}

%AMS
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{mathtools}

\usepackage{geometry}
 \geometry{a4paper,left=35mm,top=20mm,}

%environments
\newtheorem{fact}{Fact}

%abbreviations
\newcommand{\ra}{\rangle}
\newcommand{\la}{\langle}
\newcommand{\n}{\neg}
\newcommand{\et}{\wedge}
\newcommand{\jt}{\rightarrow}
\newcommand{\ko}[1]{\forall  #1\,}
\newcommand{\ro}{\leftrightarrow}
\newcommand{\exi}[1]{\exists\, {_{#1}}}
\newcommand{\pr}[1]{\mathsf{P}(#1)}
\newcommand{\cost}{\mathsf{cost}}

\newcommand{\odds}{\mathsf{Odds}}
\newcommand{\ind}{\mathsf{Ind}}
\newcommand{\nf}[2]{\nicefrac{#1\,}{#2}}
\newcommand{\R}[1]{\texttt{#1}}
\newcommand{\prr}[1]{\mbox{$\mathtt{P}_{prior}(#1)$}}
\newcommand{\prp}[1]{\mbox{$\mathtt{P}_{posterior}(#1)$}}

\newtheorem{q}{\color{blue}Question}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}

%technical intermezzo
%---------------------

\newcommand{\intermezzoa}{
	\begin{minipage}[c]{13cm}
	\begin{center}\rule{10cm}{0.4pt}

	\tiny{\sc Optional Content Starts}

	\vspace{-1mm}

	\rule{10cm}{0.4pt}\end{center}
	\end{minipage}\nopagebreak 
	}

\newcommand{\intermezzob}{\nopagebreak 
	\begin{minipage}[c]{13cm}
	\begin{center}\rule{10cm}{0.4pt}

	\tiny{\sc Optional Content Ends}

	\vspace{-1mm}

	\rule{10cm}{0.4pt}\end{center}
	\end{minipage}
	}
%--------------------

\newtheorem*{reply*}{Reply}
\usepackage{enumitem}
\newcommand{\question}[1]{\begin{enumerate}[resume,leftmargin=0cm,labelsep=0cm,align=left]
\item #1
\end{enumerate}}

@@

% \setbeamertemplate{blocks}[rounded][shadow=true]
% \setbeamertemplate{itemize items}[ball]
% \AtBeginPart{}
% \AtBeginSection{}
% \AtBeginSubsection{}
% \AtBeginSubsubsection{}
% \setlength{\emergencystretch}{0em}
% \setlength{\parskip}{0pt}

\usepackage[authoryear]{natbib}

%\bibliographystyle{apalike}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

\hypertarget{exploration}{%
\section{Exploration}\label{exploration}}

Load the dataset and take a look first.

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{summaries }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\AttributeTok{file =} \StringTok{"datasets/Summaries.csv"}\NormalTok{)}
\FunctionTok{head}\NormalTok{(summaries) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{kable}\NormalTok{( }\StringTok{"latex"}\NormalTok{, }\AttributeTok{booktabs =}\NormalTok{ T) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{kable\_styling}\NormalTok{(}\AttributeTok{latex\_options =} \FunctionTok{c}\NormalTok{(}\StringTok{"striped"}\NormalTok{, }\StringTok{"scale\_down"}\NormalTok{) ,}\AttributeTok{font\_size =} \DecValTok{9}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}
\centering\begingroup\fontsize{9}{11}\selectfont

\resizebox{\linewidth}{!}{
\begin{tabular}{rlrrrrrrrrrrlr}
\toprule
X & author & AB & AD & AA & CB & CD & CA & Adiff & Cdiff & AdiffS & CdiffS & group & IC\\
\midrule
\cellcolor{gray!6}{1} & \cellcolor{gray!6}{\_swf} & \cellcolor{gray!6}{19} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{720} & \cellcolor{gray!6}{25} & \cellcolor{gray!6}{28} & \cellcolor{gray!6}{-19} & \cellcolor{gray!6}{-692} & \cellcolor{gray!6}{-0.0245122} & \cellcolor{gray!6}{-0.3501491} & \cellcolor{gray!6}{normative} & \cellcolor{gray!6}{1}\\
2 & -Allergic & 24 & 24 & 8 & 1614 & 1451 & 1237 & -16 & -377 & 0.0719197 & 0.1057675 & normative & 3\\
\cellcolor{gray!6}{3} & \cellcolor{gray!6}{-funny-username-} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{12} & \cellcolor{gray!6}{847} & \cellcolor{gray!6}{497} & \cellcolor{gray!6}{721} & \cellcolor{gray!6}{-11} & \cellcolor{gray!6}{-126} & \cellcolor{gray!6}{0.2326395} & \cellcolor{gray!6}{0.4690535} & \cellcolor{gray!6}{control} & \cellcolor{gray!6}{0}\\
4 & -Johnny- & 18 & 2 & 8 & 1465 & 408 & 684 & -10 & -781 & 0.2647835 & -0.4789637 & empathy & 2\\
\cellcolor{gray!6}{5} & \cellcolor{gray!6}{1secwhileiyeet3} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{3} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{1384} & \cellcolor{gray!6}{198} & \cellcolor{gray!6}{120} & \cellcolor{gray!6}{-11} & \cellcolor{gray!6}{-1264} & \cellcolor{gray!6}{0.2326395} & \cellcolor{gray!6}{-1.1780359} & \cellcolor{gray!6}{control} & \cellcolor{gray!6}{0}\\
\addlinespace
6 & 20CharsIsNotEnough & 16 & 10 & 25 & 779 & 907 & 972 & 9 & 193 & 0.8755188 & 0.9307596 & empathy & 4\\
\bottomrule
\end{tabular}}
\endgroup{}
\end{table}
\normalsize

The basic variables we are dealing with are in the following table.

\begin{table}
\centering\begingroup\fontsize{9}{11}\selectfont

\begin{tabular}{ll}
\toprule
variable & explanation\\
\midrule
\cellcolor{gray!6}{AB} & \cellcolor{gray!6}{attacks before (pre-treatment)}\\
AD & attacks during (the treatment period)\\
\cellcolor{gray!6}{AA} & \cellcolor{gray!6}{attacks after (post-treatment)}\\
CB & comments before\\
\cellcolor{gray!6}{CD} & \cellcolor{gray!6}{comments during}\\
\addlinespace
CA & comments after\\
\cellcolor{gray!6}{group} & \cellcolor{gray!6}{treatment group}\\
IC & intervention count\\
\bottomrule
\end{tabular}
\endgroup{}
\end{table}

Further variables are defined in terms of those, in particular, we will
be predicting \textsf{AdiffS} which is the standardized difference
\textsf{AA}-\textsf{AB}, and \textsf{AdiffS}, which is the standardized
difference \textsf{CA}-\textsf{CB}. Before we proceed, we will also
standardize the predictors, and add a numerical index for the group:

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{ABS }\OtherTok{\textless{}{-}} \FunctionTok{standardize}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{AB)}
\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{CBS }\OtherTok{\textless{}{-}} \FunctionTok{standardize}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{CB)}
\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{AAS }\OtherTok{\textless{}{-}} \FunctionTok{standardize}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{AA)}
\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{CAS }\OtherTok{\textless{}{-}} \FunctionTok{standardize}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{CA)}
\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{CDS }\OtherTok{\textless{}{-}} \FunctionTok{standardize}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{CD)}
\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{ADS }\OtherTok{\textless{}{-}} \FunctionTok{standardize}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{AD)}
\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{group }\OtherTok{\textless{}{-}} \FunctionTok{as.factor}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{group)}
\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{groupID }\OtherTok{\textless{}{-}}  \FunctionTok{as.integer}\NormalTok{( }\FunctionTok{as.factor}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{group) )}
\end{Highlighting}
\end{Shaded}

@@

First, let's take a look at the distribution of \textsf{IC} in the
treatment groups:

@@

Crucially, all backdoor paths go through \textsf{ADS}, which then
becomes either a fork or a pipe, so all backdoor paths can be closed by
conditioning on \textsf{ADS}. Moreover there is only one directed
indirect path, it goes through \textsf{CAS}, so we should not condition
on it if we are to identify causal effect on attacks mediated by impact
on comments (unless we care about the direct effect of \textsf{IC} and
\textsf{IT} on \textsf{AAS}, but that's a separate question). This is in
line with the adjustment set identified algorithmically.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  10pt,
  dvipsnames, enabledeprecatedfontcommands]{scrartcl}
\title{Bayesian analysis of the NESTA study of interventions against
verbal aggression online \linebreak  Technical Report}
\author{Rafal Urbaniak}
\date{}

@@

  pdftitle={Bayesian analysis of the NESTA study of interventions against verbal aggression online Technical Report},

@@

\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}

@@

\usepackage{wrapfig}

@@

\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures

@@

\hypertarget{data-and-exploration}{%
\section{Data and exploration}\label{data-and-exploration}}

\vspace{1mm}
\scriptsize

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{Hate }\OtherTok{\textless{}{-}} \FunctionTok{readRDS}\NormalTok{(}\AttributeTok{file =} \StringTok{"datasets/RAWNESTA/Hate.rds"}\NormalTok{)}
\NormalTok{Comments }\OtherTok{\textless{}{-}} \FunctionTok{readRDS}\NormalTok{(}\AttributeTok{file =} \StringTok{"datasets/RAWNESTA/Comments.rds"}\NormalTok{)}
\NormalTok{summaries }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\AttributeTok{file =} \StringTok{"datasets/Summaries.csv"}\NormalTok{)}

\NormalTok{dates }\OtherTok{\textless{}{-}} \FunctionTok{colnames}\NormalTok{(Hate)[}\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{]}
\NormalTok{dates }\OtherTok{\textless{}{-}} \FunctionTok{as.Date}\NormalTok{(dates)}
\NormalTok{startDate }\OtherTok{\textless{}{-}}\NormalTok{ dates[}\DecValTok{1}\NormalTok{]}
\NormalTok{interventionDate }\OtherTok{\textless{}{-}} \StringTok{"2020{-}07{-}08"}
\NormalTok{observationDate }\OtherTok{\textless{}{-}} \StringTok{"2020{-}09{-}09"}
\NormalTok{end }\OtherTok{\textless{}{-}}\NormalTok{ dates[}\FunctionTok{length}\NormalTok{(dates)]}

\NormalTok{periods }\OtherTok{\textless{}{-}} \FunctionTok{numeric}\NormalTok{(}\FunctionTok{length}\NormalTok{(dates))}
\NormalTok{periods }\OtherTok{\textless{}{-}} \FunctionTok{ifelse}\NormalTok{(dates }\SpecialCharTok{\textless{}}\NormalTok{ interventionDate, }\StringTok{"pre{-}treatment"}\NormalTok{, periods)}
\NormalTok{periods }\OtherTok{\textless{}{-}} \FunctionTok{ifelse}\NormalTok{(dates }\SpecialCharTok{\textgreater{}=}\NormalTok{ interventionDate }\SpecialCharTok{\&}\NormalTok{ dates }\SpecialCharTok{\textless{}}\NormalTok{ observationDate,}
    \StringTok{"treatment"}\NormalTok{, periods)}
\NormalTok{periods }\OtherTok{\textless{}{-}} \FunctionTok{ifelse}\NormalTok{(dates }\SpecialCharTok{\textgreater{}=}\NormalTok{ observationDate, }\StringTok{"post{-}treatment"}\NormalTok{, periods)}

\NormalTok{hateTS }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(}\FunctionTok{colSums}\NormalTok{(Hate[, }\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{]))}
\NormalTok{hateTS}\SpecialCharTok{$}\NormalTok{date }\OtherTok{\textless{}{-}} \FunctionTok{as.Date}\NormalTok{(}\FunctionTok{rownames}\NormalTok{(hateTS))}
\FunctionTok{rownames}\NormalTok{(hateTS) }\OtherTok{\textless{}{-}} \ConstantTok{NULL}
\FunctionTok{colnames}\NormalTok{(hateTS) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"attacks"}\NormalTok{, }\StringTok{"date"}\NormalTok{)}
\NormalTok{hateTS}\SpecialCharTok{$}\NormalTok{periods }\OtherTok{\textless{}{-}}\NormalTok{ periods}

\NormalTok{interventions }\OtherTok{\textless{}{-}} \FunctionTok{readRDS}\NormalTok{(}\AttributeTok{file =} \StringTok{"datasets/interventions.rds"}\NormalTok{)}
\NormalTok{interventionsTS }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(}\FunctionTok{table}\NormalTok{(interventions}\SpecialCharTok{$}\NormalTok{day))}
\NormalTok{interventionsTS}\SpecialCharTok{$}\NormalTok{Var1 }\OtherTok{\textless{}{-}} \FunctionTok{as.Date}\NormalTok{(interventionsTS}\SpecialCharTok{$}\NormalTok{Var1)}
\FunctionTok{colnames}\NormalTok{(interventionsTS) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"date"}\NormalTok{, }\StringTok{"interventions"}\NormalTok{)}

\NormalTok{periodsDF }\OtherTok{\textless{}{-}} \FunctionTok{merge}\NormalTok{(}\AttributeTok{x =}\NormalTok{ hateTS, }\AttributeTok{y =}\NormalTok{ interventionsTS, }\AttributeTok{by =} \StringTok{"date"}\NormalTok{, }\AttributeTok{all.x =} \ConstantTok{TRUE}\NormalTok{)}

\NormalTok{idx }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\FunctionTok{diff}\NormalTok{(periodsDF}\SpecialCharTok{$}\NormalTok{date))}
\NormalTok{i2 }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\FunctionTok{which}\NormalTok{(idx }\SpecialCharTok{!=} \DecValTok{1}\NormalTok{), }\FunctionTok{nrow}\NormalTok{(periodsDF) }\SpecialCharTok{+} \DecValTok{1}\NormalTok{)}
\NormalTok{periodsDF}\SpecialCharTok{$}\NormalTok{grp }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{1}\SpecialCharTok{:}\FunctionTok{length}\NormalTok{(}\FunctionTok{diff}\NormalTok{(i2)), }\FunctionTok{diff}\NormalTok{(i2))}

\NormalTok{periodsDF}\SpecialCharTok{$}\NormalTok{interventions[}\FunctionTok{is.na}\NormalTok{(periodsDF}\SpecialCharTok{$}\NormalTok{interventions) }\SpecialCharTok{\&}\NormalTok{ periodsDF}\SpecialCharTok{$}\NormalTok{periods }\SpecialCharTok{==}
    \StringTok{"treatment"}\NormalTok{] }\OtherTok{\textless{}{-}} \DecValTok{0}

\NormalTok{periodsPlot }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(periodsDF) }\SpecialCharTok{+} \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ date, }\AttributeTok{y =}\NormalTok{ attacks,}
    \AttributeTok{group =}\NormalTok{ grp), }\AttributeTok{alpha =} \FloatTok{0.8}\NormalTok{, }\AttributeTok{size =} \FloatTok{0.6}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ date, }\AttributeTok{y =}\NormalTok{ interventions,}
    \AttributeTok{group =}\NormalTok{ grp), }\AttributeTok{alpha =} \FloatTok{0.8}\NormalTok{, }\AttributeTok{size =} \FloatTok{0.6}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{geom\_vline}\NormalTok{(}\AttributeTok{xintercept =}\NormalTok{ startDate,}
    \AttributeTok{lty =} \DecValTok{2}\NormalTok{, }\AttributeTok{size =} \FloatTok{0.2}\NormalTok{, }\AttributeTok{alpha =} \FloatTok{0.5}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{geom\_vline}\NormalTok{(}\AttributeTok{xintercept =} \FunctionTok{as.Date}\NormalTok{(interventionDate),}
    \AttributeTok{lty =} \DecValTok{2}\NormalTok{, }\AttributeTok{size =} \FloatTok{0.2}\NormalTok{, }\AttributeTok{alpha =} \FloatTok{0.5}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{geom\_vline}\NormalTok{(}\AttributeTok{xintercept =} \FunctionTok{as.Date}\NormalTok{(observationDate),}
    \AttributeTok{lty =} \DecValTok{2}\NormalTok{, }\AttributeTok{size =} \FloatTok{0.2}\NormalTok{, }\AttributeTok{alpha =} \FloatTok{0.5}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{geom\_vline}\NormalTok{(}\AttributeTok{xintercept =} \FunctionTok{as.Date}\NormalTok{(end),}
    \AttributeTok{lty =} \DecValTok{2}\NormalTok{, }\AttributeTok{size =} \FloatTok{0.2}\NormalTok{, }\AttributeTok{alpha =} \FloatTok{0.5}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Attacks and interventions time series"}\NormalTok{,}
    \AttributeTok{subtitle =} \StringTok{"no line at data gaps"}\NormalTok{, }\AttributeTok{caption =} \StringTok{"days with data: 81 (pre{-}treatment), 62 (treatment), 72 (post{-}treatment)"}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{theme\_tufte}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{theme}\NormalTok{(}\AttributeTok{axis.title.x =} \FunctionTok{element\_blank}\NormalTok{(), }\AttributeTok{plot.caption =} \FunctionTok{element\_text}\NormalTok{(}\AttributeTok{hjust =} \FloatTok{0.5}\NormalTok{,}
    \AttributeTok{face =} \StringTok{"italic"}\NormalTok{)) }\SpecialCharTok{+} \FunctionTok{scale\_x\_date}\NormalTok{(}\AttributeTok{date\_labels =} \StringTok{"\%b \%d"}\NormalTok{, }\AttributeTok{breaks =} \FunctionTok{c}\NormalTok{(startDate,}
    \FunctionTok{as.Date}\NormalTok{(startDate), }\FunctionTok{as.Date}\NormalTok{(interventionDate), }\FunctionTok{as.Date}\NormalTok{(observationDate),}
\NormalTok{    end), }\AttributeTok{limits =} \FunctionTok{c}\NormalTok{(startDate }\SpecialCharTok{{-}} \DecValTok{30}\NormalTok{, end }\SpecialCharTok{+} \DecValTok{10}\NormalTok{)) }\SpecialCharTok{+} \FunctionTok{ylab}\NormalTok{(}\StringTok{"count"}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{annotate}\NormalTok{(}\StringTok{"rect"}\NormalTok{,}
    \AttributeTok{xmin =} \FunctionTok{as.Date}\NormalTok{(interventionDate), }\AttributeTok{xmax =} \FunctionTok{as.Date}\NormalTok{(observationDate),}
    \AttributeTok{ymin =} \SpecialCharTok{{-}}\DecValTok{1}\NormalTok{, }\AttributeTok{ymax =} \DecValTok{360}\NormalTok{, }\AttributeTok{alpha =} \FloatTok{0.2}\NormalTok{, }\AttributeTok{fill =} \StringTok{"darkgreen"}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{ylim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{,}
    \DecValTok{370}\NormalTok{)) }\SpecialCharTok{+} \FunctionTok{annotate}\NormalTok{(}\StringTok{"text"}\NormalTok{, }\AttributeTok{label =} \StringTok{"pre{-}treatment"}\NormalTok{, }\AttributeTok{x =} \FunctionTok{as.Date}\NormalTok{(startDate) }\SpecialCharTok{+}
    \DecValTok{2}\NormalTok{, }\AttributeTok{y =} \DecValTok{370}\NormalTok{, }\AttributeTok{hjust =} \DecValTok{0}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{annotate}\NormalTok{(}\StringTok{"text"}\NormalTok{, }\AttributeTok{label =} \StringTok{"treatment"}\NormalTok{, }\AttributeTok{x =} \FunctionTok{as.Date}\NormalTok{(interventionDate) }\SpecialCharTok{+}
    \DecValTok{2}\NormalTok{, }\AttributeTok{y =} \DecValTok{370}\NormalTok{, }\AttributeTok{hjust =} \DecValTok{0}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{annotate}\NormalTok{(}\StringTok{"text"}\NormalTok{, }\AttributeTok{label =} \StringTok{"post{-}treatment"}\NormalTok{,}
    \AttributeTok{x =} \FunctionTok{as.Date}\NormalTok{(observationDate) }\SpecialCharTok{+} \DecValTok{2}\NormalTok{, }\AttributeTok{y =} \DecValTok{370}\NormalTok{, }\AttributeTok{hjust =} \DecValTok{0}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{annotate}\NormalTok{(}\StringTok{"text"}\NormalTok{,}
    \AttributeTok{label =} \StringTok{"interventions:"}\NormalTok{, }\AttributeTok{x =} \FunctionTok{as.Date}\NormalTok{(interventionDate) }\SpecialCharTok{{-}} \DecValTok{55}\NormalTok{, }\AttributeTok{y =} \DecValTok{15}\NormalTok{,}
    \AttributeTok{hjust =} \DecValTok{0}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{annotate}\NormalTok{(}\StringTok{"text"}\NormalTok{, }\AttributeTok{label =} \StringTok{"attacks:"}\NormalTok{, }\AttributeTok{x =} \FunctionTok{as.Date}\NormalTok{(startDate) }\SpecialCharTok{{-}}
    \DecValTok{30}\NormalTok{, }\AttributeTok{y =} \DecValTok{215}\NormalTok{, }\AttributeTok{hjust =} \DecValTok{0}\NormalTok{)}

\NormalTok{periodsDF}\SpecialCharTok{$}\NormalTok{weekdays }\OtherTok{\textless{}{-}} \FunctionTok{weekdays}\NormalTok{(}\FunctionTok{as.Date}\NormalTok{(periodsDF}\SpecialCharTok{$}\NormalTok{date))}
\NormalTok{periodsDF}\SpecialCharTok{$}\NormalTok{weeks }\OtherTok{\textless{}{-}} \FunctionTok{week}\NormalTok{(}\FunctionTok{as.Date}\NormalTok{(periodsDF}\SpecialCharTok{$}\NormalTok{date))}

\NormalTok{periodsDF}\SpecialCharTok{$}\NormalTok{weekdays }\OtherTok{\textless{}{-}} \FunctionTok{as.factor}\NormalTok{(periodsDF}\SpecialCharTok{$}\NormalTok{weekdays)}
\FunctionTok{levels}\NormalTok{(periodsDF}\SpecialCharTok{$}\NormalTok{weekdays) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{,}
    \StringTok{"Friday"}\NormalTok{, }\StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)}
\NormalTok{weeksPlot }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(periodsDF) }\SpecialCharTok{+} \FunctionTok{geom\_smooth}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ weekdays, }\AttributeTok{y =}\NormalTok{ attacks,}
    \AttributeTok{group =} \DecValTok{1}\NormalTok{)) }\SpecialCharTok{+} \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ weekdays, }\AttributeTok{y =}\NormalTok{ attacks, }\AttributeTok{group =}\NormalTok{ weeks),}
    \AttributeTok{alpha =} \FloatTok{0.1}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{theme\_tufte}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Personal attacks throught weekdays (six months)"}\NormalTok{,}
    \AttributeTok{subtitle =} \StringTok{"No weekly patterns"}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{xlab}\NormalTok{(}\StringTok{""}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{ylab}\NormalTok{(}\StringTok{"count"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

For the duration of the project we selected 486 Reddit users and tracked
their activity (with some breaks resulting from API restrictions and
technical issues, which were mostly sorted out in the observation
period), starting on \texttt{r}startDate`, beginning the intervention
period on 2020-07-08, leading to a further observation period starting
on 2020-09-09 and ending on 2020-11-20. The time series of attacks
observed and of interventions conducted can be inspected in Figure
\ref{fig:periodsPlot}.

\begin{figure}[H]

\begin{center}\includegraphics[width=1\linewidth]{technicalReport4_files/figure-latex/periodsPlot-1} \end{center}
\caption{Daily sums of attacks and interventions throughout the three experimental periods, with GAM smoothing (blue).}
\label{fig:periodsPlot}
\end{figure}

Interestingly, no weekly patterns of overall aggressive behavior seem
apparent, as can be seen from plotting multiple weeks alongside, as in
Figure \ref{fig:weeksPlot}.

\begin{figure}[H]

\begin{center}\includegraphics[width=1\linewidth]{technicalReport4_files/figure-latex/weeksPlot-1} \end{center}
\caption{Attack sums from all  weeks in the experimental period plotted against week days. No pattern seems to arise.}
\label{fig:weeksPlot}
\end{figure}

We analyzed the data from two perspective: we ran a before-and after
analysis, comparing the summarized aggression levels before and after
the intervention period (with various additional predictors), and a
time-series perspective, which took a more fine-grained perspective. For
now, we will focus on the Bayesian before-and-after analysis, for which
the data were cleaned and converted into a summarized form, involving
the variables listed in Table \ref{tab:baaVars}.

@@

\begin{table}
\centering
\begin{tabular}{ll}
\toprule
variable & explanation\\
\midrule
\cellcolor{gray!6}{AB} & \cellcolor{gray!6}{attacks before (pre-treatment)}\\
AD & attacks during (the treatment period)\\
\cellcolor{gray!6}{AA} & \cellcolor{gray!6}{attacks after (post-treatment)}\\
CB & comments before\\
\cellcolor{gray!6}{CD} & \cellcolor{gray!6}{comments during}\\
CA & comments after\\
\cellcolor{gray!6}{group} & \cellcolor{gray!6}{treatment group}\\
IC & intervention count\\
\bottomrule
\end{tabular}

\caption{Variables involved in the before-and-after analysis.}
\label{tab:baaVars}
\end{table}

Further variables were defined in terms of those, in particular, we will
be predicting \textsf{AdiffS} which is the standardized difference
\textsf{AA}-\textsf{AB}, and \textsf{AdiffS}, which is the standardized
difference \textsf{CA}-\textsf{CB}. The predictors were also
standardized (and named \(\langle\)variable\char`\_name\(\rangle\)S),
and a numerical index for the group (\textsf{groupID}) has been
introduced.

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{ABS }\OtherTok{\textless{}{-}} \FunctionTok{standardize}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{AB)}
\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{CBS }\OtherTok{\textless{}{-}} \FunctionTok{standardize}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{CB)}
\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{AAS }\OtherTok{\textless{}{-}} \FunctionTok{standardize}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{AA)}
\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{CAS }\OtherTok{\textless{}{-}} \FunctionTok{standardize}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{CA)}
\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{CDS }\OtherTok{\textless{}{-}} \FunctionTok{standardize}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{CD)}
\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{ADS }\OtherTok{\textless{}{-}} \FunctionTok{standardize}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{AD)}
\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{group }\OtherTok{\textless{}{-}} \FunctionTok{as.factor}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{group)}
\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{groupID }\OtherTok{\textless{}{-}} \FunctionTok{as.integer}\NormalTok{(}\FunctionTok{as.factor}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{group))}
\end{Highlighting}
\end{Shaded}

@@

The distribution of \textsf{IC} in the treatment groups is visualized in
Figure \ref{fig:interventionsDistro}. Note that the distributions are
somewhat different, even though the total intervention counts are
similar (110 for empathy and 119 for normative). The issue is discussed
in Section XXXXX.

@@
